A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-10-19 doc/large_strain.tex
provisional fix for linearization part

In order to solve \eqref{eq:weak_form} using Newton's method, a first order approximation around a given solution field $\overline{\gz u}$ is required such that
\begin{align}
F(\overline{\gz u} + \Delta \gz u, \delta \gz u) \approx
F(\overline{\gz u}, \delta \gz u) + \D_{\Delta \gz u} F(\overline{\gz u}, \delta \gz u).
\end{align}
For conservative traction boundary conditions, the directional derivative is given by
\begin{align}
\D_{\Delta \gz u}  F(\overline{\gz u}, \delta \gz u)
=
\int_{\mcl B_0} \D_{\Delta \gz u} \gz \tau : \overline{\grad^s} \, \delta \gz u \, \d V
+
\int_{\mcl B_0} \overline{\gz \tau} : \left[ \Grad \, \delta \gz u \cdot \D_{\Delta \gz u}  \gz F^{-1} \right] \d V.
\end{align}
Following \cite{Wriggers2008}, this can be simplified to
\begin{align}
\D_{\Delta \gz u} F(\overline{\gz u}, \delta \gz u)
  =
  \int_{\mcl B_0} \overline{\grad^s} \Delta \gz u : J \boldsymbol{\mathcal{C}} : \overline{\grad^s} \, \delta \gz u \, \d V
  +
  \int_{\mcl B_0}
  \overline{\grad}\delta \gz u :
  \left[
  \overline{\grad} \Delta \gz u \cdot
  \overline{\gz \tau}
  \right]
  \d V.
\label{eq:tangent}
\end{align}
Here $\overline{(\bullet)}$ is used to denote quantities evaluated using the displacement field $\overline {\gz u}$, and the fourth-order tangent tensor is the push forward of the material tangent $J \boldsymbol{\mathcal{C}} = \chi\left( 4 \frac{d^{2} \psi \left( \mathbf{C} \right)}{d \mathbf{C} \otimes d \mathbf{C}} \right)$. The first term in \eqref{eq:tangent} is related to the linearization of the Kirchhoff stress and therefore called material part of the tangent operator.  The second term in \eqref{eq:tangent} is called geometric part of the tangent since it originates from the linearization of the inverse of the deformation gradient $\gz F^{-1}$.

>>>>

In order to solve \eqref{eq:weak_form} using Newton's method, a first order approximation around a given solution field $\overline{\gz u}$ is required such that
\begin{align}
F(\overline{\gz u} + \Delta \gz u, \delta \gz u) \approx
F(\overline{\gz u}, \delta \gz u) + \D_{\Delta \gz u} F(\overline{\gz u}, \delta \gz u) \cdot \Delta \gz u.
\end{align}
For conservative traction boundary conditions, the directional derivative is given by
\begin{equation}
\begin{split}
\D_{\Delta \gz u}  F(\overline{\gz u}, \delta \gz u) \cdot \Delta \gz u
&=
\int_{\mcl B_0} \left[\D_{\Delta \gz u} \gz \tau \cdot \Delta \gz u\right] : \overline{\grad^s} \, \delta \gz u \, \d V
\\
& +
\int_{\mcl B_0} \overline{\gz \tau} : \left[ \Grad \, \delta \gz u \cdot
\left[\D_{\Delta \gz u}  \gz F^{-1} \cdot \Delta \gz u\right]
\right] \d V.
\end{split}
\end{equation}
Following \cite{Wriggers2008}, this can be simplified to
\begin{equation}
  \begin{split}
\D_{\Delta \gz u} F(\overline{\gz u}, \delta \gz u) \cdot \Delta \gz u
  &=
  \int_{\mcl B_0} \overline{\grad^s} \Delta \gz u : J \boldsymbol{\mathcal{C}} : \overline{\grad^s} \, \delta \gz u \, \d V \\
  &+
  \int_{\mcl B_0}
  \overline{\grad}\delta \gz u :
  \left[
  \overline{\grad} \Delta \gz u \cdot
  \overline{\gz \tau}
  \right]
  \d V.
\end{split}
\label{eq:tangent}
\end{equation}
Here $\overline{(\bullet)}$ is used to denote quantities evaluated using the displacement field $\overline {\gz u}$, and the fourth-order tangent tensor is the push forward of the material tangent $J \boldsymbol{\mathcal{C}} = \chi\left( 4 \frac{d^{2} \psi \left( \mathbf{C} \right)}{d \mathbf{C} \otimes d \mathbf{C}} \right)$. The first term in \eqref{eq:tangent} is related to the linearization of the Kirchhoff stress and therefore called material part of the tangent operator.  The second term in \eqref{eq:tangent} is called geometric part of the tangent since it originates from the linearization of the inverse of the deformation gradient $\gz F^{-1}$.
